Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
Some proofreading of page 5 and 6

The predictor combination yielding the lowest value of the Akaike information criterion
included the following parameters.

@@

As the regression table above shows, it seems that substituting the
Decision Tree classifier for the Naive Bayes baseline provides the
most significant boost to our f measure. It can also be seen here that
increasing the collocation window will increase the f measure by about 0.003
for each additional word added to the window. Additionally, enabling
the cooccurrence feature extractor with the Naive Bayes classifier
will increase the f measure by a significant amount as well.

The rows that contain negative terms may indicate that the interacting
features provide similar functionality. That is, the enabled features
are interfering with each other so that their final influence on the f
measure may affect the f measure negatively. For instance, the row
showing ``classifiert:collocation'' indicates a run where the Decision
Tree classifier was used and the collocation feature was enabled has
resulted in a lower accuracy. This seems to be the general trend for
all of the interacting features. It may be interesting to note that
the interaction between collocation and cooccurrence1 as well as
collocation and dependency parsing produce the most innocuous
cumulative effect. Perhaps this may be why collocation and
cooccurrence are often advocated to be used together.

>>>>

The predictor combination yielding the lowest value of the Akaike information criterion
included the following parameters:

@@

As the regression table above shows, it seems that substituting the
Decision Tree classifier for the \naive{} Bayes baseline provides the
most significant boost to our f-measure. It can also be seen here that
increasing the collocation window will increase the f-measure by about 0.003
for each additional word added to the window. Additionally, enabling
the co-occurrence feature extractor with the Naive Bayes classifier
will increase the f-measure by a significant amount as well.

The rows that contain negative terms may indicate that the interacting
features provide similar functionality. That is, the enabled features
are interfering with each other so that their final influence on the
f-measure may affect the f-measure negatively. For instance, the row
showing ``classifiert:collocation'' indicates a run where the Decision
Tree classifier was used and the collocation feature was enabled has
resulted in a lower accuracy. This seems to be the general trend for
all of the interacting features. It may be interesting to note that
the interaction between collocation and cooccurrence1 as well as
collocation and dependency parsing produce the most innocuous
cumulative effect. Perhaps this may be why collocation and
co-occurrence are often advocated to be used together.
